<!--
%\VignetteEngine{knitr::knitr}
%\VignetteIndexEntry{poster}
-->

# Using the poster package

[libpostal](https://github.com/openvenues/libpostal) is a postal address parser written in C - and `poster` is a wrapper around it, allowing you to parse and normalise addresses from R.

## Installation

Installing `poster` is pretty easy - just run `install_github` or `install.packages` as appropriate - as long as you've got `libpostal` on your system. Installing libpostal can be done with the following; on Linux:

```
sudo apt-get install curl libsnappy-dev autoconf automake libtool pkg-config
git clone https://github.com/openvenues/libpostal
cd libpostal
./bootstrap.sh
./configure --datadir=[...some dir with a few GB of space...]
make
sudo make install
sudo ldconfig
```

On Macs:

```
sudo brew install snappy autoconf automake libtool pkg-config
git clone https://github.com/openvenues/libpostal
cd libpostal
./bootstrap.sh
./configure --datadir=[...some dir with a few GB of space...]
make
sudo make install
```

`libpostal` doesn't run on Windows - and correspondingly `poster` won't.

## Features

The fastest and simplest feature of `poster` is an address normaliser, which does what it says on the tin: uses statistics to try and turn the awkward, vague, inconsistent addresses human beings put into forms into a standard format. This can be handled with the `normalise_addr` function:

```{r, eval=FALSE}
normalise_addr("Quatre-vignt-douze Ave des Champs-Élysées")
[1] "4-vignt-12 avenue des champs-elysees"
```

More importantly, `poster` can also *parse* addresses, standardising it and splitting it up into everything from the house name or number to the postal code and country:

```{r, eval=FALSE}
str(parse_addr("781 Franklin Ave Crown Heights Brooklyn NYC NY 11216 USA"))
'data.frame':	1 obs. of  10 variables:
 $ house         : chr NA
 $ house_number  : chr "781"
 $ road          : chr "franklin ave"
 $ suburb        : chr "crown heights"
 $ city_district : chr "brooklyn"
 $ city          : chr "nyc"
 $ state_district: chr NA
 $ state         : chr "ny"
 $ postal_code   : chr NA
 $ country       : chr "usa"
```

As well as parse the entire address, you can also extract individual elements: there are functions with names matching the columns in `parse_addr`'s output (`house`, `house_number`, `country`) that extract those individual elements.

## Issues and suggestions

If you have ideas for other functionality, the best approach is to either [request it](https://github.com/Ironholds/poster/issues) or [add it](https://github.com/Ironholds/poster/pulls)!
